
%________________________________________________________________________________________
% @brief    LaTeX2e Resume for Qingpeng Zhang
% @author   Qingpeng Zhang
% @date     Nov 2014
% @info     Based on Latex Resume Template by Chris Paciorek 
%           http://www.stat.berkeley.edu/~paciorek/computingTips/Latex_template_creating_CV_.html



\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{url}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Qingpeng Zhang \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{3in}}
Department of Computer Science and Engineering  & {\it Phone:}  (678) 901-9911 \\            
Michigan State University & {\it E-mail:} \url{qingpeng@msu.edu} \\       
428 S. Shaw Ln., RM 3115 & {\it Web:} \url{http://www.cse.msu.edu/~qingpeng/} \\ 
East Lansing, MI  48824 USA  & {\it Twitter:} \href{http://twitter.com/qingpengzhang}{@qingpengzhang}\\     
\end{tabular}


\section{\sc Research Interests}

Broadly my research interest is developing and applying scalable computational tools to enable investigations of large, complex biological dataset.

My dissertation developed approaches to investigate the diversity of various complex metagenomic samples based on k-mer counting algorithms.  

\section{\sc Education}
{\bf Michigan State University}, {\em Department of Computer Science and 
Engineering,} East Lansing, USA\\
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Candidate, Computer Science and Quantitative Biology (Dual Major)
\begin{list2}
\vspace*{.05in}
    \item Dissertation Topic:  ``A Novel Computational Approach to Investigate
    Microbial Diversity using Whole-genome Shotgun Metagenomic Data'' 
    \item Advisor:  C. Titus Brown
    \item Anticipated Graduation Spring 2015
\end{list2}
\end{list1}

{\bf Nanjing University}, {\em Department of Physics,} Nanjing, China\\
\vspace*{-.1in}
\begin{list1}
\item[] B.S., Physics (Biophysics),  July, 2003
\end{list1}


\section{\sc Research Experience}
{\bf Michigan State University}, Department of Computer Science and 
Engineering, East Lansing, USA

{\em Graduate Research Assistant} in GED Lab (Advisor: C. Titus Brown),
\hfill {\bf August, 2008 - present}

\begin{list2}

    \item developed an efficient k-mer counting software package – 
    khmer. [1]
    \item developed digital normalization approach for scaling shotgun seq analysis [2]
    \item investigated the genomic versatility and functional variation 
    between two heterotrophic symbionts of deep-sea Osedax worms. [3]
    \item the development of novel methods required for diversity measurement 
    of extremely large metagenomics samples. [Manuscript in preparation]
\end{list2}

{\bf Chinese Academy of Sciences}, Institute of Genetics and Developmental 
Biology, Beijing, China

{\em Research Staff in Bioinformatics} in Han Lab (Advisor: Jing-Dong Jackie 
Han), \hfill {\bf May, 2005 - July, 2008}

\begin{list2}

    \item identified the proliferation/differentiation switch in the 
    cellular network of multicellular organisms. [5]
    \item investigated the regulatory circuitry of aging. [4]
    \item identified microRNA/siRNA in human intron region using 
    Bayesian classifier.
\end{list2}

{\bf BGI-Beijing}, Bioinformatics Department, Beijing, China

{\em Research Staff in Bioinformatics} \hfill {\bf July, 2003 - May, 2005}

\begin{list2}

    \item silkworm genome sequencing project as core member of the genomic 
    analysis group. [7]
    \item assembled and analyzed deer BAC clones. [6]
\end{list2}

\section{\sc Publications}

{\em up-to-date publication list at: http://scholar.google.com/citations?user=3TddZSQAAAAJ}\\

\begin{enumerate}

\item {\em These are not the k-mers you are looking for: efficient online 
k-mer counting using a probabilistic data structure.} {\bf Qingpeng Zhang}, Jason Pell, Rosangela Canino-Koning, Adina Chuang Howe, C. 
Titus Brown. PLOS ONE, July 25, 2014, 
\href{http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0101271}{DOI: 10.1371/journal.pone.0101271}

\item {\em A Reference-Free Algorithm for Computational Normalization of Shotgun 
Sequencing Data.} C. Titus Brown, Adina Howe, {\bf Qingpeng Zhang}, Alexis B. Pyrkosz, Timothy H. 
Brom.  submitted. http://arxiv.org/abs/1203.4802

\item {\em Genomic versatility and functional variation between two dominant 
heterotrophic symbionts of deep-sea Osedax worms.} Shana K Goffredi, Hana Yi, 
{\bf Qingpeng Zhang}, Jane E Klann, Isabelle A Struve, Robert C Vrijenhoek and 
C Titus Brown. The ISME Journal , (14 November 2013) | 
doi:10.1038/ismej.2013.201

\item {\em A Modular Network Model of Aging.} Xue H, Xian B, Dong D, Xia K, Zhu S, 
Zhang Z, Hou L, {\bf Zhang Q}, Zhang Y, Han J-D J.  Molecular Systems 
Biology, 2007, 3: 147.

\item {\em Identification of the Proliferation/Differentiation Switch in the 
Cellular Network of Multicellular Organisms.} Kai Xia, Huiling 
Xue, Dong Dong, Shanshan Zhu, Jiamu Wang, {\bf Qingpeng Zhang}, 
Lei Hou, Hua Chen, Ran Tao, Zheng Huang, Zheng Fu, Ye-Guang Chen, and 
Jing-Dong J Han PLoS Comput Biol. 2006 Nov 24;2(11):e145

\item {\em Comparative genomic analysis links karyotypic evolution with genomic 
evolution in the Indian Muntjac (Muntiacus muntjak vaginalis).} Qi Zhou, 
Ling Huang, Jianguo Zhang, Xiangyi Zhao, {\bf Qingpeng Zhang}, Fei Song, 
Jianxiang Chi, Fengtang Yang and Wen Wang Chromosoma. 
2006 Dec;115(6):427-436. Epub 2006 Jun 22.

\item {\em A Draft Sequence for the Genome of the Domesticated Silkworm (Bombyx mori)
} Science. 2004 Dec 10;306(5703):1937-40 (list author)

\end{enumerate}

\section{\sc Conference Presentations}
\begin{list2}
\item {\em A probabilistic approach to k-mer counting.} Annual Bioinformatics Open 
Source Conference (BOSC2012) July 2012, Long Beach, USA
\end{list2}


\section{\sc Teaching Experience}

\begin{list2}

\item Teaching Assistant of EDAMAME Workshop - Explorations in Data Analyses for Metagenomic Advances in Microbial Ecology, Kellogg Biological Station, Michigan State University, August 2014
\item Teaching Assistant of MSU NGS Summer Course - Analyzing Next-Generation Sequencing Data, Kellogg Biological Station, Michigan State University, August 2014
\item Instructor of Software Carpentry Workshop at Wuhan Institute of Virology, Chinese Academy of Sciences, China, July 2013
\item Teaching Assistant of Software Carpentry Workshop at The Scripps Research Institute, La Jolla, CA, November 2012
\item Teaching Assistant of MSU NGS Summer Course - Analyzing Next-Generation Sequencing Data, Kellogg Biological Station, Michigan State University, June 2012
\item Teaching Assistant of CSE491 - Introduction to Database-Backed Web Development, Department of Computer Science and Engineering, Michigan State University, 2008 Fall, 2012 Spring
\item Teaching Assistant of CSE231 - Introduction to Programming I -Python, Department of Computer Science and Engineering, Michigan State University, 2010 Spring, 2010 Fall, 2011 Spring, 2012 Fall, 2013 Spring

\end{list2}

\section{\sc Professional Training}

\begin{list1}

\item[] Selected Courses (at Michigan State University)

\begin{list1}
\vspace*{.05in}
\item[]  CSE 824 Advanced Computer Networks and Communications
\item[]  CSE 830 Design and Theory of Algorithms
\item[]  CSE 847 Machine Learning
\item[]  CSE 860 Foundations of Computing
\item[]  CSE 881 Data Mining
\item[]  CSE 891 Probabilistic Models and Algorithms in Computational Biology
\item[]  CSE 891 Open Problems in Bioinformatics
\item[]  QB 826 Introduction to Quantitative Biology Techniques
\item[]  QB 827 Problems in Quantitative Biology
\item[]  QB 828 Biology for the Interdisciplinary Scientist
\item[]  MMG 890 Environmental Metagenomics

\end{list1}
\vspace*{.1in}

\item[] Workshops and Conferences (as attendee or poster presenter)

\begin{list1}
\vspace*{.05in}
\item[]  2014.10 The 6th Annual Argonne Soil Metagenomics Meeting, Chicago, IL, USA
\item[]  2014.04 Software Carpentry Instructor Training Workshop, Toronto, Canada
\item[]  2014.04 PyCon2014, Montreal, Canada
\item[]  2012.07 Annual Bioinformatics Open Source Conference (BOSC2012) Long Beach, CA, USA
\item[]  2012.07 20th Annual International Conference on Intelligent Systems for Molecular Biology (ISMB2012) Long Beach, CA, USA
\item[]  2012.05 Great Lakes Bioinformatics Conference 2012 (GLBIO2012) Ann Arbor, MI, USA
\item[]  2012.05 Frontiers in Metagenomics Symposium, Columbia, MO, USA
\item[]  2011.06 The First International Earth Microbiome Project Conference, Shenzhen, China
\item[]  2010.05 Certification in College Teaching Institute, East Lansing, MI, USA
\item[]  2009.05 Google Developer Days 2009, Beijing, China
\item[]  2007.03 International Networking for Young Scientists (INYS) Workshop on computational biology, Beijing, China 
\item[]  2006.10 International Conference on Genomics, Hangzhou, China

\end{list1}
\end{list1}


\section{\sc Honors and Awards} 

\begin{list1}

\item[] 2009-2014 CSE Summer Research Fellowship, Michigan State University
\item[] 2008 Quantitative Biology(QB) Recruiting Fellowship, Michigan State University
\item[] 2003 Honored Graduate Award, Nanjing University (3\% of all graduates) 
\item[] 1999-2001 Scholarship for Annually Excellent Student, Nanjing University (20\% of all students) 
\item[] 1999 First Grade Scholarship for Freshman, Nanjing University (5\% of all freshmen)

\end{list1}


\section{\sc References} 

{\em ( Contact details available upon request.)}

Dr. C. Titus Brown, Associate Professor, University of California, Davis, ctbrown@ucdavis.edu

Dr. James Cole, Assistant Professor, Michigan State University, colej@msu.edu 

Dr. Adina Chuang Howe, Assistant Professor, Iowa State University, achuang@engineering.uiowa.edu

\end{resume}
\end{document}




